\title{Dependent variable definitions}
\begin{description}
\item[Homicide rate]: No. of homicide victims aged 0 to 19 years per 100,000 popln.
\item[Any violent discipline]: Percentage in age 2 to 14 years who experienced any 
violent discipline(psychological aggression and/or physical punishment) in the past month.
\item[Physical punishment]: Percentage in age 2 to 14 years who experienced physical punishment
in the past month.
\item[Psychological aggression]: Percentage in age 2 to 14 years who experienced psychological 
aggression in the past month.
\item[Bullying]: Percentage of adolescents aged 13 to 15 years who reported being bullied at
least once in the past couple of months.
\item[Physical fights]: Percentage of adolescents aged 13 to 15 years who reported being in 
a physical fight one or more times during the past 12 months.
\item[Physical attacks]: Percentage of students aged 13 to 15 years who reported being physically 
attacked one or more times in
the past 12 months.
\item[Experience of physical violence since age 15]: Percentage of girls and boys aged 15 to 19 years 
who experienced any physical violence since age 15.
\item[Lifetime experience of sexual violence]: Percentage of girls and boys aged 15 to 19 years who ever
experienced forced sexual intercourse or any other forced sexual acts
\item[Intimate partner violence]: Percentage of ever-married girls and boys aged 15 to 19 years who ever experienced any
physical, sexual or emotional violence committed by their
spouses or partners.
\item[Attitudes towards wife-beating]: Percentage of girls and boys aged 15 to 19 years who think that a husband/partner is justified in hitting or beating his wife/partner 
\item[Attitudes towards physical punishment]: Percentage of adults who think that physical punishment is necessary to raise/educate children.
\end{description}